The K2 Bright Star Survey I: Methodology and Data Release

### 2019-07-03 paper/ms.tex
capitalize dbscan

In addition to expanding the range of possible objective functions, we have also added a feature `\texttt{deathstar}' to deal with contamination. Clusters of pixels are identified with the DBSCAN algorithm \citep[Density-based spatial clustering of applications with noise;][]{dbscan}, and we join these clusters with the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2}. Clusters other than the target star identified by this algorithm are identified as possible background sources and removed from the target pixel file before processing. Other than this, we have adopted less-aggressive quality flagging, having found that many cadences were being classified as bad quality for spurious `cosmic ray' events, which were actually caused by a combination of saturation and spacecraft motion. We instead chose to iteratively sigma-clip outliers and retain cadences with the \texttt{lightkurve} default quality mask.

>>>>

In addition to expanding the range of possible objective functions, we have also added a feature `\texttt{deathstar}' to deal with contamination. Clusters of pixels are identified with the DBSCAN algorithm \citep[Density-Based Spatial Clustering of Applications with Noise;][]{dbscan}, and we join these clusters with the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2}. Clusters other than the target star identified by this algorithm are identified as possible background sources and removed from the target pixel file before processing. Other than this, we have adopted less-aggressive quality flagging, having found that many cadences were being classified as bad quality for spurious `cosmic ray' events, which were actually caused by a combination of saturation and spacecraft motion. We instead chose to iteratively sigma-clip outliers and retain cadences with the \texttt{lightkurve} default quality mask.
